---
title: "Software Carpentry Workshop Example"
author: "Martina Morris"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette 
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  
---

This is meant to demostrate the use of a git repo along with R, and knitr/markdown

I was hoping to keep the .md file with "keep_md: true" but i'm not sure how to specify that in the YAML code above.

## Vignette Info

Here we will show how to write a function to summarize some data

## Data

The data here come from [NOAA](http://www.ncdc.noaa.gov/qclcd/QCLCD), and I've downloaded the December 2015 dailies for Sand Point (in Seattle).  The datafile is in the repo, and it's called QCLData.txt

## Function

The function summarizes data from an arbitrary file -- the filename is the argument to the function -- but the data from NOAA was sufficiently hinky that the commands in the function really only work with that one file... 

```{r, fig.show='hold'}
summarize <- function(datafile) {
  mydir <- "../"  # data directory
  rawdata <- read.csv(paste(mydir, datafile, sep=""), header=T, na.strings="M") #read it in
  aaa <- rawdata[,c("Tmax","Tmin", "Tavg", "Depart")] #subset
  
#  par(mfrow=c(1,2))  
  plot(aaa$Tmin, aaa$Tmax, pch="@", col="red",
       main="Dec 2015 Daily Temps", xlab="Min", ylab="Max")
  abline(lm(aaa$Tmax ~ aaa$Tmin))
  
  plot(aaa$Depart, col="blue",
       main="Departure from Average", xlab="Date", ylab="Degrees")
  abline(h=0, col="red")
  
  meanvec <- colMeans(aaa, na.rm=TRUE)
  print(round(meanvec,2))
  
  return(meanvec)
}
```

So, now let's use the function:

```{r}
summarize("QCLData.txt")
```

Voila!

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
